%-------------------------
% Resume in Latex
% Author : Nidhi Gupta
% Based off of: https://github.com/Kumari-Nidhi-Gupta/resume.git
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Nidhi Gupta} \\ \vspace{1pt}
    \small 6388191496 $|$ \href{mailto:kumarinidhi6388@gmail.com}{{kumarinidhi6388@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/nidhi-gupta-a269231b0/}{{linkedin.com/in/Nidhi}}
\end{center}

%-----------Professional Summary-----------
\section{Professional Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{}{Software Developer with expertise in PHP, Laravel, CI and back-end technologies, having 3 years of experience in developing scalable web applications.} \\
 \end{itemize}
 
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Front End}{: AngularJS (Basic)} \\
      \textbf{Back End}{: PHP} \\
      \textbf{Frameworks}{: Laravel, CodeIgniter, CakePHP (Basic), WordPress} \\
      \textbf{Website Technologies}{: HTML, CSS, Bootstrap, JavaScript, jQuery, AJAX} \\
      \textbf{Database}{: MySQL} \\
      \textbf{Code Versioning }{: Git, GitHub} \\
      \textbf{Containerization}{: Docker} \\
      \textbf{Cloud Platforms}{: AWS (EC2)} \\
     }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{December 2023 – Present}
      {TechExe IT Solutions Pvt. Ltd.}{Lucknow, India}
      \resumeItemListStart
        \resumeItem{Developing and maintaining scalable web applications using Laravel and Core PHP.}
        \resumeItem{Integrating APIs and third-party services to enhance functionality.}
        \resumeItem{Applying SOLID principles and Strategy Pattern for maintainable and efficient code.}
        \resumeItem{Optimizing MySQL queries and managing databases.}
        \resumeItem{Using GitHub for version control and team collaboration.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{November 2021 – December 2023}
      {Jamtech Technologies Pvt. Ltd.}{Lucknow, India}
      \resumeItemListStart
        \resumeItem{Developed web applications using Laravel, CodeIgniter, AngularJS, and WordPress.}
        \resumeItem{Optimized database performance and managed cloud deployments on AWS (EC2, Forge).}
        \resumeItem{Customized WordPress themes and plugins.}
        \resumeItem{Implemented real-time communication using socket.io.}
      \resumeItemListEnd

    \resumeSubheading
      {Computer Operator}{June 2020 – February 2021}
      {AsthaJyoti Info and Placement Services Pvt. Ltd.}{Lucknow, India}
      \resumeItemListStart
        \resumeItem{Managed data entry, document processing, and company records.}
        \resumeItem{Assisted in website updates using PHP and MySQL.}
      \resumeItemListEnd

    \resumeSubheading
      {Web Developer}{August 2019 – March 2020}
      {What’s New Technology}{Lucknow, India}
      \resumeItemListStart
        \resumeItem{Learned and worked with CodeIgniter (CI) at the start of my career.}
        \resumeItem{Performed website maintenance, bug fixes, and security updates.}
      \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{Yamini Cultural Institute} $|$ \emph{Core PHP}}{}
        \resumeItemListStart
            \resumeItem{Developed an online learning platform for music and dance enthusiasts.}
            \resumeItem{Designed a user-friendly interface allowing users to register, enroll, and take courses.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Orange Moon Student Safety Services} $|$ \emph{Laravel}}{}
        \resumeItemListStart
            \resumeItem{Built a student safety management platform with roles for Admin, Clients, and Monitors.}
            \resumeItem{Integrated real-time communication using socket.io.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Book Your Own (BYO)} $|$ \emph{Laravel}}{}
        \resumeItemListStart
            \resumeItem{Developed a hotel booking system integrated with Google Hotel Center and channel managers.}
            \resumeItem{Implemented cab booking functionality and advanced search filters.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{GoodFish} $|$ \emph{Angular, WordPress}}{}
        \resumeItemListStart
            \resumeItem{Built a dating platform with enhanced privacy features.}
            \resumeItem{Developed user profiles, daily questions, and secure chat functionality.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{QL \& DUMO} $|$ \emph{Laravel}}{}
        \resumeItemListStart
            \resumeItem{Developed a parent-child learning app with course purchase and personalized recommendations.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Stallion Warehouse Management} $|$ \emph{Laravel (Repository-based)}}{}
        \resumeItemListStart
            \resumeItem{Built a warehouse management system with Shopify integrations, webhooks, and APIs.}
            \resumeItem{Implemented multi-role access for Admins, 3PL, and Customers.}
        \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MG Institute of Management \& Technology}{Lucknow, Uttar Pradesh}
      {Bachelor of Technology (Computer Science \& Engineering) - AKTU}{2020 – 2023}
    \resumeSubheading
      {Government Girls Polytechnic}{Gorakhpur, Uttar Pradesh}
      {Diploma (Information Technology) - BTEUP}{2016 – 2019}
    \resumeSubheading
      {Jyoti Inter College}{Gorakhpur, Uttar Pradesh}
      {12th - UP Board}{2015 – 2016}
    \resumeSubheading
      {B.K.H.S Pipraich}{Gorakhpur, Uttar Pradesh}
      {10th - UP Board}{2013 – 2014}
  \resumeSubHeadingListEnd


%----------DECLARATION------------
\section{DECLARATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {I hereby declare that all the information provided above is correct and true to my knowledge.
}{} {} {}{Nidhi Gupta}


\end{document}
